\documentclass[letter]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{stmaryrd}

%% Sets page size and margins
\usepackage[top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{array}
\usepackage[shortlabels]{enumitem}
\usepackage[final]{pdfpages}
\usepackage[normalem]{ulem}
\usepackage{cancel}
\usepackage{xspace,mdwlist}
\usepackage{algorithmic}
\usepackage{mathtools}
\usetikzlibrary{calc}

\usepackage{courier} %% Sets font for listing as Courier.
\usepackage{listings, xcolor}
\lstset{
tabsize = 4, %% set tab space width
showstringspaces = false, %% prevent space marking in strings, string is defined as the text that is generally printed directly to the console
numbers = left, %% display line numbers on the left
commentstyle = \color{green}, %% set comment color
keywordstyle = \color{blue}, %% set keyword color
stringstyle = \color{red}, %% set string color
rulecolor = \color{black}, %% set frame color to avoid being affected by text color
basicstyle = \small \ttfamily , %% set listing font and size
breaklines = true, %% enable line breaking
numberstyle = \tiny,
}



\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

\newtheorem{theorem}{Theorem}[section]
\newtheorem*{claim}{Claim}
\DeclareMathOperator*{\argmin}{\arg\!\min}

\def\coursename{CS 201: Data Structures}

%% make title box
\newcommand{\header}[1]{%
	\begin{center}
		\fbox{
			\begin{minipage}{6in}
				\textbf{\coursename} \hfill       \\
				\textit{#1} \hfill \textit{\today}
			\end{minipage}
		}
	\end{center}
	\vspace*{4mm}
}

\def\problem#1#2#3{
\fbox{
\begin{minipage}{0.8\textwidth}
{\sc #1:}

\begin{description*}
\item[Given:] #2
\item[Find:] #3
\end{description*}
\end{minipage}
}
\bigskip
}


\begin{document}

\header{Week 2}

\begin{enumerate} [1.]
    \item 
    \begin{itemize}
        \item [(a)] True/false : method overriding is when we modify an inherited method, so that the method in the subclass has different behavior from that of the superclass. 
        \item [(b)] 1b) True/false : method overloading is when we have more than one method with the same signature but different behavior. 
        \item [(c)] 1c True/false : static methods can access instance variables, but can’t modify them. 
        \item [(d)] 1d) Suppose Shape is an interface and Rectangle is a class implementing the interface Shape. What is the difference between x and y, in terms of what methods they can use?
        
        
        Shape x = new Rectangle();\\
        Rectangle y = new Rectangle();
    \end{itemize}

    \item How does an interface differ from a class implementation? (Question from Carrano)

    \item Write an interface for a Plant. Classes implementing Plant must be able to report their height and be watered (have their water level increase an integer amount).


    \item Write a class Sunflower that implements Plant. 
    
    Instance variables:
    \begin{enumerate}
        \item height
        \item height
        \item numSeeds - the number of seeds in a Sunflower object.
    \end{enumerate}
    
    Methods:
    \begin{enumerate}
        \item All methods specified by the Plant interface
        \item howManySeeds() - returns numSeeds
    \end{enumerate}
    
    \item Suppose I have a variable collection, which is a Plant[] array that stores different objects that implement the interface Plant. One of those objects is a Sunflower. Write a code to find which index of the Plant[] array contains a Sunflower object. If that index contains a Sunflower object, print out the index and the number of seeds.

    
\end{enumerate}
\end{document}